---
title: "Hackathon - Sprint 1"
output: html_notebook
---

# Library
```{r}
library(tidyverse) # for everything :)
library(readxl) # for reading in xls docs
library(VIM) # for aggr
library(ggplot2) # for vis
library(cluster)
library(fpc)
```

# Hypothesis

NULL: Generations do not take different amounts of time off from work. There is no identifiable clusters of absences that can be attributed to age.

# Import your data
Watch out for the file extension here...
```{r}
df <- read_xls("downloads/Absenteeism_at_work.xls")
```

# Transform & Explore

Take a look at your data using `head`
```{r}
head(df)
```

Trying running some `summary` stats
```{r}
summary(df)
```

Check for missing values. You might need the `VIM` package for this.
```{r}
aggr(df)
```

Create a view of the individual rather than a view of the absenses.
```{r}
df <- aggregate(df, by=list(df$ID), FUN=mean)
```

Take another look at head
```{r}
head(df)
```

Normalise the dataset
```{r}
## TBD
```


Run clustering using K-means
```{r}
# Kmeans cluster analysis
cluster <- kmeans(df, centers=6)
# Plot cluster to see whether k-means has rationally clustered
plotcluster(df, cluster$cluster)
```

Check-out the head to see any identifiable patterns. 
```{r}
head(cluster)
```

Create an elbow graph to 
```{r}
k.max <- 15
data <- df
wss <- sapply(1:k.max, 
              function(k){kmeans(data, k, nstart=50,iter.max = 15 )$tot.withinss})
wss
plot(1:k.max, wss,
     type="b", pch = 19, frame = FALSE, 
     xlab="Number of clusters K",
     ylab="Total within-clusters sum of squares")
```

Create a new dataframe with the same info as `df` and add in the results of the k-means clustering
```{r}
kmeansResult<-factor(cluster$cluster)
df2 <- df
df2$cluster <- kmeansResult
```

Check out the new dataframe with clustered classes
```{r}
df2
```

```{r}

```

